Classical Planning with Simulators: \\ Results on the Atari Video Games

### 2015-02-11 ijcai15-paper/paper.tex
typos fixed by nir

Also,  as reported by  BNVB, all of the algorithms 
reuse the frames in the sub-tree of the previous lookahead that is rooted in the selected 
child, deleting its siblings and their descendants. More precisely, no calls 
to the emulator are done for transitions that are cached in that sub-tree, 
and such reused frames are not discounted from the budget that is thus a bound 
on the number of \emph{new}  frames per lookahead. In addition, in $\IW(1)$, the states that 
are reused  from the previous searches are ignored in the computation of the novelty of 
new states so that more states can escape pruning. Otherwise, $\IW(1)$ often
uses a fraction of the  budget.  This is not needed in \BFS\ which does 
no pruning.  $\IW(1)$ and \BFS\ are  limited to  search up to a depth of
$m=1,500$ frames and up to $m=150,000$ frames per root branch. This is
to avoid the search from  going too deep or being too committed to a
single root action. 
% Similarly UCT defines a limit of $m=300$ frames for each rollout. 
% Note that UCT is more likely to have a performance
% loss if the depth is increased, as the number of rollouts would
% decrease in order to maintain the same budget of $150,000$ simulated
% frames.

@@

$\IW(1)$ obtains better scores than the best learning algorithm in
\cite{deep-mind-atari} in the $7$ games considered there, and
\BFS\ does so in $6$ of the $7$ games. Comparing with the scores reported for the reinforcement learning algorithms in BNVB,
we note that both $\IW(1)$ and \BFS\ do much better than the best learning algorithm in
those games where the learning algorithms outperform \UCT\, namely, \Montezuma, \Venture\
and \Bowling. We take this as evidence that $\IW(1)$ and \BFS\ are as at least as good as learning
algorithms at finding rewards in games where \UCT\ is not very effective.

>>>>

Also,  as reported by  BNVB, all of the algorithms 
reuse the frames in the sub-tree of the previous lookahead that is rooted in the selected 
child, deleting its siblings and their descendants. More precisely, no calls 
to the emulator are done for transitions that are cached in that sub-tree, 
and such reused frames are not discounted from the budget that is thus a bound 
on the number of \emph{new}  frames per lookahead. In addition, in $\IW(1)$, the states that 
are reused  from the previous searches are ignored in the computation of the novelty of 
new states so that more states can escape pruning. Otherwise, $\IW(1)$ often
uses a fraction of the  budget.  This is not needed in \BFS\ which does 
no pruning.  $\IW(1)$ and \BFS\ are  limited to  search up to a depth of
$1,500$ frames and up to $150,000$ frames per root branch. This is
to avoid the search from  going too deep or being too committed to a
single root action. 
% Similarly UCT defines a limit of $m=300$ frames for each rollout. 
% Note that UCT is more likely to have a performance
% loss if the depth is increased, as the number of rollouts would
% decrease in order to maintain the same budget of $150,000$ simulated
% frames.

@@

$\IW(1)$ obtains better scores than the best learning algorithm
\cite{deep-mind-atari} in the $7$ games considered there, and
\BFS\ does so in $6$ of the $7$ games. Comparing with the scores reported for the reinforcement learning algorithms in BNVB,
we note that both $\IW(1)$ and \BFS\ do much better than the best learning algorithm in
those games where the learning algorithms outperform \UCT\, namely, \Montezuma, \Venture\
and \Bowling. We take this as evidence that $\IW(1)$ and \BFS\ are as at least as good as learning
algorithms at finding rewards in games where \UCT\ is not very effective.
